### 2022-04-23 paper/ase22/experiment.tex
exp

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate sentences consistent to their
  sentiment label and their target \lc?
\item \label{rq:two}: Can the \tool generated testcases have stronger
  generalization ability to test NLP models?
\item \label{rq:three}: Can \tool be useful to find root of bug in the
  NLP models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

To answer the RQs, we need to show: (\romnum{1}) correctness of testcase to
evaluate its target \lc.  (\romnum{2}) effect of testcase distribution on
finding bugs; (\romnum{3}) degree of execution of a NLP model on testcases;
and (\romnum{4}) ability to guide to find cause of bug in a NLP
model.

First, \tool generates sentences and its label by empirical reasoning
derived from \lc statements. Therefore, we meaure acceptibility of the
testcases by verifying the relevancy between sentence and label, and
between sentence and its \lc. The RQ~\ref{rq:one} thereby is answered
by verifying the quality of generated testcases. In this work, we
conduct manual study and measure the correlation of human labeled
testcases and \tool labeled testcases. Second, the amount of NLP model
component executed during testing is a critical measurement for
assessing quality of software testing. A high software coverage
results in higher chances of unidentified bugs in the NLP model. On
the other hand, limited distribution only represents narrow portion of
real world covering limited execution behaviors in a NLP model. It leads
to detect bugs within the restricted execution behaviors.  Therefore,
testcases more equivalent to real world represents more generalized
distribution, and it results in high coverage of the NLP model.
Accordingly, the ability of testcases to produce high portion of model
coverage needs to be measured. We answer the RQ~\ref{rq:three}
measuring neural coverage of the neural NLP model according to the
measurements. In addition to the detection of bugs in the model,
explaination of the bugs is also important stage of debugging and
repairing the model. Therefore, we anwer RQ~\ref{rq:three} by showing
usefulness of \tool by analyzing the NLP model based on \tool and
finding root of the bug.

@@

\subsubsection*{\textbf{Model Coverage}}
We implement DeepXplore to measure the NLP model
coverage~\cite{pei2017deepxplore}. \Dxp is the first efficient
whitebox testing framework for large-scale \dl systems. It introduces
neuron coverage of a set of test inputs as the ratio of the number of
unique activated neurons and the total number of neurons in input \dl
system. In this experiment, we compute the neuron coverage of a test
cases from \tool and \Cklst on the fine-tuned \sa model of
\bertsamodel and compare the coverage between \tool and \Cklst.

>>>>

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate sentences consistent to their
  sentiment label and their target \lc?
\item \label{rq:two}: Can the \tool generated testcases have stronger
  generalization ability to test \sa models?
\item \label{rq:three}: Can \tool be useful to find root of bug in the
  \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

To answer the RQs, we need to show: (\romnum{1}) correctness of testcase to
evaluate its target \lc.  (\romnum{2}) effect of testcase distribution on
finding bugs; (\romnum{3}) degree of execution of a \sa model on testcases;
and (\romnum{4}) ability to guide to find cause of bug in a \sa
model.

First, \tool generates sentences and its label by empirical reasoning
derived from \lc statements. Therefore, we meaure acceptibility of the
testcases by verifying the relevancy between sentence and label, and
between sentence and its \lc. The RQ~\ref{rq:one} thereby is answered
by verifying the quality of generated testcases. In this work, we
conduct manual study and measure the correlation of human labeled
testcases and \tool labeled testcases. Second, the amount of \sa model
component executed during testing is a critical measurement for
assessing quality of software testing. A high software coverage
results in higher chances of unidentified bugs in the \sa model. On
the other hand, limited distribution only represents narrow portion of
real world covering limited execution behaviors in a \sa model. It leads
to detect bugs within the restricted execution behaviors.  Therefore,
testcases more equivalent to real world represents more generalized
distribution, and it results in high coverage of the \sa model.
Accordingly, the ability of testcases to produce high portion of model
coverage needs to be measured. We answer the RQ~\ref{rq:three}
measuring neural coverage of the neural \sa model according to the
measurements. In addition to the detection of bugs in the model,
explaination of the bugs is also important stage of debugging and
repairing the model. Therefore, we anwer RQ~\ref{rq:three} by showing
usefulness of \tool by analyzing the \sa model based on \tool and
finding root of the bug.

@@

\subsubsection*{\textbf{Model Coverage}}
We implement DeepXplore to measure the \sa model
coverage~\cite{pei2017deepxplore}. \Dxp is the first efficient
whitebox testing framework for large-scale \dl systems. It introduces
neuron coverage of a set of test inputs as the ratio of the number of
unique activated neurons and the total number of neurons in input \dl
system. In this experiment, we compute the neuron coverage of a test
cases from \tool and \Cklst on the fine-tuned \sa model of
\bertsamodel and compare the coverage between \tool and \Cklst.

\subsubsection*{\textbf{Analysis of Root of bug}}
In this experiment, we analyze a \sa model based on the test results
of the set of \tool test inputs and find the root of bug in the
model. It shows that \tool generated testcases are useful to explain
the \sa model test results and identify the rationale of the bug
found. We implement \Denas for this experiment. Rules generated from
\Denas is interpretable functions mapping certain features of the
input to the expected output of a deep \nn system, and the generated
rules are considered as the behaviors of the deep \nn system. To
anlayze the bug of a \sa model, we generates rules over the test
inputs using \Denas and identifies falty rules for the failed test
inputs. We manually identify the root of the falty rules and find the
root of bug in the end.
